Prepare SSURGO Data

### 2023-07-29 Codes/0_7_ssurgo.Rmd
change the aquifer thickness threshold to 9

  return(ssurgo_data_sum)
}

@@

parallel::mclapply(
  1:nrow(all_counties),
  \(x) {
    print(x)
    file_name <- here::here(paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds"))
    if (!file.exists(file_name)) {
      print(paste0("working on ", x))
      temp <- get_ssurgo_props(all_counties[x, ], vars)
      saveRDS(temp, here::here(paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds")))
    } else {
      print(paste0("skipping ", x))
    }
  },
  mc.cores = 6,
  mc.preschedule = FALSE
)

# lapply(
#   1:nrow(all_counties),
#   \(x) {
#     print(x)
#     file_name <- paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds")
#     if (!file.exists(file_name)) {
#       temp <- get_ssurgo_props(field = all_counties[x, ], vars)
#       saveRDS(temp, paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds"))
#     }
#   }
# )
```

@@

```{r }
ssurgo_soil <-
  fs::dir_ls("Shared/Data/RawData/SSURGO") %>%
  purrr::map(readRDS) %>%
  lapply(function(x) x[, geometry := NULL]) %>%
  rbindlist() %>%
  .[, `:=`(
    state = NULL,
    state_name = NULL,
    ir_area_ratio = NULL,
    in_hpa = NULL
  )]

saveRDS(ssurgo_soil, here("Shared/Data/ProcessedData/ssurgo_soil.rds"))
# all_counties[, state_name] %>% unique()
```

>>>>

  ssurgo_data_sum[, sc_code := field$sc_code]
  return(ssurgo_data_sum)
}

@@

parallel::mclapply(
  1:nrow(all_counties),
  \(x) {
    print(x)
    file_name <- here::here(paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds"))
    if (!file.exists(file_name)) {
      print(paste0("working on ", x))
      temp <- get_ssurgo_props(all_counties[x, ], vars)
      saveRDS(temp, here::here(paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds")))
    } else {
      temp <- readRDS(file_name)
      if (ncol(temp) < 7) {
        temp <- get_ssurgo_props(field = all_counties[x, ], vars)
        saveRDS(temp, paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds"))
      } else {
        print(paste0("skipping ", x))
      }
    }
  },
  mc.cores = 6,
  mc.preschedule = FALSE
)

lapply(
  1:nrow(all_counties),
  \(x) {
    print(x)
    file_name <- paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds")
    if (!file.exists(file_name)) {
      temp <- get_ssurgo_props(field = all_counties[x, ], vars)
      saveRDS(temp, paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds"))
    } else {
      temp <- readRDS(file_name)
      if (ncol(temp) < 7) {
        temp <- get_ssurgo_props(field = all_counties[x, ], vars)
        saveRDS(temp, paste0("Shared/Data/RawData/SSURGO/ssurgo_", x, "rds"))
      }
    }
  }
)
```

@@

```{r }
ssurgo_soil <-
  fs::dir_ls("Shared/Data/RawData/SSURGO") %>%
  purrr::map(readRDS) %>%
  rbindlist()

saveRDS(ssurgo_soil, here("Shared/Data/ProcessedData/ssurgo_soil.rds"))
```
